RQdraft2

### 2024-09-16 RQdraft2.Rmd
ch8menuinsert

-   Journal prestige
-   Gender homphily
-   Age
-   repeated publications
-   nr of publications
-   Dutch or English text publications
-   gender segregation and field of publication (journal field)

@@

# Research Questions

**RQ1a:**

To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?

@@

-   (1a+b needed? Would like more concise, not ask uneccessary questions)
-   (2&3 seem random and disconnected; Journal prestige of interest tho, how to best include?)
-   (necessity to have RQ3 that asks about structural networks effects?)

@@

    1.  What homophily preferences determine research collaborations among higher education researchers?

    ```{=html}
    <!-- -->
    ```
    2.  What are the most powerful homophily indicators in research collaborations in higher education research?

@@

>>>>

@@

# Research Questions (old, replace with new ones!)

RQ1a: To what extent does gender homophily occur across all co-publications of the staff of the Sociology Department and Political Science Department at Radboud University?

@@

@@

    -

        (1) What homophily preferences determine research collaborations among higher education researchers?

    -

        (2) What are the most powerful homophily indicators in research collaborations in higher education research?

@@

# Data types needed for research

+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
| Variable                           | Potential measurement                                   | Notes                                                                                                  |
+====================================+=========================================================+========================================================================================================+
| **Actor attributes**               |                                                         |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
| Gender                             | Google Scholar: \                                       | What about gender neutral names? If we go by this principle, then gender neutral names = non-binary ?? |
|                                    | Name ➙ Look up in gendered list whether Woman or Man    |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
|                                    | Linked-in: \                                            | Not everyone puts their pronouns on linkedin\                                                          |
|                                    | Pronouns                                                | And: not everyone who uses e.g. She/her pronouns is a Woman                                            |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
| High prestige publication (prior)  | If the author had a publication in a journal that ....\ |                                                                                                        |
|                                    | before the publication of the paper in question         |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
| **Relational Attributes**          |                                                         |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
| Initiation of the co-authorship    | First author of paper = initiator                       |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
| Paper                              | A paper people have co-authorship on                    | How prevent from counting double? \                                                                    |
|                                    |                                                         | Overall: systematic approach to webscrape?                                                             |
|                                    | Signifier: DOI?                                         |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+
|                                    |                                                         |                                                                                                        |
+------------------------------------+---------------------------------------------------------+--------------------------------------------------------------------------------------------------------+

: Data types
